A parralelized and distributed approach to implementing Conway's Game of Life

### 2022-11-29 report/article_2.tex
more content

\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\blindtext % Dummy text
%------------------------------------------------

@@

@@

@@

@@

@@

@@

>>>>

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item use built in golang benchmark framework
  \item run command ....
  \item output to txt
  \item run python script to plot graphs
  \item barchart of time taken against threads used
  \item runs benchmarks on all pgm images
  \item repeats benchmarks until results fall within a certain standard deviation (TBC)
\end{itemize}
%------------------------------------------------

@@

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show workers pseudocode
  \item show handler pseudocode
  \item flowchart/ diagram of how channel communication workers
  \item simple flowchart of how the whole program works currently
\end{itemize}
%------------------------------------------------

@@

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show graph for 5120x5120.gpm for single implementation vs parralel implementation
  \item describe the differences between each graph
  \item explain the differences by referencing the flowchart/ how the code worker
  \item explain the shape of the graph (why it resembles a 1/x graph). e.g. bottlenecks in channel communication...
\end{itemize}
%------------------------------------------------

@@

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
THIS SECTION WILL BE USED IF WE DECIDE TO IMPLEMENT MEMORY SHARING OVER CHANNEL COMMUNICATION
%------------------------------------------------

@@

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
TO BE IMPLEMENTED
%------------------------------------------------

@@

\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
TO BE IMPLEMENTED
%------------------------------------------------

@@

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show graphs and describe shape and differences of with vs without SDL
  \item explain how SDL works
  \item explain how this causes bottlenecks
\end{itemize}
%------------------------------------------------
